Under-ice acoustic navigation using real-time model-aided range estimation

### 2022-02-20 manuscript/main.tex
fix bibs for intro

Thorough reviews of uncrewed vehicle operations in polar environments can be found in \citep{Norgren2014} and \citep{Barker2020}; there is no comparable work in the Arctic for a short range AUV deployment in the Beaufort Lens.
Seminal \citep{brooke1981arcs,jackson1983autonomous,light1989autonomous,bellingham1995auv,hayes2002determining} and more recent AUV deployments \citep{Jakuba2008,Kunz2008,}\citep{jakuba_2008_long,kunz_deep_2008,kukulya2010under,plueddemann_autonomous_2012,timmermans2013scales,fossum2021adaptive} witnessed the classical upward refracting sound speed profile that is amenable to an isovelocity assumption.

@@

The results from this paper derive from data taken while deploying the AUV \emph{Macrura}, a custom Bluefin-21, during the Ice Exercise 2020 (ICEX20), in the Beaufort Sea, from March 8 to 11, in double-ducted and ice-covered conditions.
The AUV deployment was supported by the Integrated Communication and Navigation Network (ICNN) \citep{Schneider2020,Randeni2020,randeni_high-resolution_2021}, a specialized implementation of the LBL solution.
The ICNN was initially developed via numerous virtual experiments to push the boundaries of algorithms and interfaces between different hardware components.
The simulation approach serves as a testbed for robustness to produce better results than post-processing previous field data.
The simulation capabilities are largely physics-driven with a modular system of systems approach\textemdash an environmental simulator with sub-components for the ocean, including Arctic ice drift and ocean acoustic propagation; a vehicle simulator with sub-components for vehicle dynamics and navigation; a topside hardware simulator and acoustic communications simulator, both with a software-only configuration and a hardware-in-the-loop version \citep{Schneider2018}.
The virtual environment similarly emulates the interfaces between the real components to test the entire software pipeline.
Both simulation capabilities are integral to mission success.

>>>>

Thorough reviews of uncrewed vehicle operations in polar environments can be found in \citep{Norgren2014} and \citep{Barker2020}; there is no comparable work in the Arctic for a short range AUV deployment in the Beaufort Lens.
Seminal \citep{brooke1981arcs,jackson1983autonomous,light1989autonomous,bellingham1995auv,hayes2002determining} and more recent AUV deployments \citep{Jakuba2008,Kunz2008,kukulya2010under,plueddemann_autonomous_2012,timmermans2013scales,fossum2021adaptive} witnessed the classical upward refracting sound speed profile that is amenable to an isovelocity assumption.

@@

The results from this paper derive from data taken while deploying the AUV \emph{Macrura}, a custom Bluefin-21, during the Ice Exercise 2020 (ICEX20), in the Beaufort Sea, from March 8th to 11th.
The AUV deployment was supported by the Integrated Communication and Navigation Network (ICNN) \citep{Schneider2020,Randeni2020,randeni_high-resolution_2021}, a specialized implementation of the LBL solution.
The ICNN was initially developed via numerous virtual experiments to push the boundaries of algorithms and interfaces between different hardware components.
The simulation approach serves as a testbed for robustness to produce better results than post-processing previous field data.
The simulation capabilities are largely physics-driven with a modular system of systems approach\textemdash an environmental simulator with sub-components for the ocean, including Arctic ice drift and ocean acoustic propagation; a vehicle simulator with sub-components for vehicle dynamics and navigation; a topside hardware simulator and acoustic communications simulator, both with a software-only configuration and a hardware-in-the-loop version \citep{Schneider2018}.
The virtual environment similarly emulates the interfaces between the real components to test the entire software pipeline.
Both simulation capabilities are integral to mission success.
